---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE)
```

[![Linux Build Status](https://travis-ci.org/metacran/rversions.svg?branch=master)](https://travis-ci.org/metacran/rversions)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/metacran/rversions?svg=true)](https://ci.appveyor.com/project/gaborcsardi/rversions)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/rversions)](http://r-pkg.org/pkg/rversions)
[![CRAN version](http://www.r-pkg.org/badges/version/rversions)](http://r-pkg.org/pkg/rversions)

# rversions — past and present R versions

The R version numbers and dates are extracted from the
main R SVN repository at http://svn.r-project.org/R/.

## Installation

```{r eval = FALSE}
install.packages("rversions")
```

## Usage

### R-release and R-oldrel

```{r}
library(rversions)
r_release()
r_oldrel()
```

### All R versions and release dates

```{r}
r_versions()
```


## Use cases in the wild

### In R packages

* `rversions` is used in `devtools`, in [`dr_devtools()`](https://devtools.r-lib.org/reference/dr_devtools.html) to compare the installed R version to the current R release version.

* [`provisionr`](https://github.com/mrc-ide/provisionr) imports `rversions` and uses it in `check_r_version()`, a function that checks and coerces something into an R version.

### In other tools

- [r-appveyor web service uses `rversions` to determine what versions r-release and r-oldrel are](https://github.com/krlmlr/r-appveyor/blob/master/scripts/appveyor-tool.ps1#L77-L87).

- R-hub uses it to do the same on [Solaris](https://github.com/r-hub/solarischeck/blob/d3edc6077f52081a53b2ed8b9ec40e17176fdb43/run.sh#L105), [macOS](https://github.com/r-hub/macoscheck/blob/846f87d1ad1c4b4aeb283a986e084913f203879f/run.sh#L160) and [Windows](https://github.com/r-hub/wincheck/blob/591ea8d9a28cd5044c063e88f46ef0507fa16fc7/run.ps1#L114).

- [R-hub's Windows install script uses it as well, to decide what versions of R to install](https://github.com/r-hub/rhub-server/blob/master/jenkins/scripts/windows-2008-setup.ps1#L74-L79).

## License

MIT © [Gábor Csárdi](http://gaborcsardi.org)
